---
title: "breaking news story"
editor: visual
---

Below is an example of a breaking news story with inline R code embedded into the body of the story.

First I downloaded the necessary packages.

```{r}
library(tidyverse)
library(lubridate)
library(readxl)
library(writexl)
library(janitor)
```

Next, I uploaded the Democrat impeachment data set. Then I filtered for individuals for and against impeachment, summarized, and saved the data to separate variables: dem_yes_impeach and dem_no_impeach. After creating the two variables, I embedded them into the news story below using the coding format \`r\`.

```{r}
impeach <- readRDS("impeach.rds")

dem_no_impeach <- impeach %>% 
  filter(for_impeachment == "NO") %>% 
  summarise(n())

dem_yes_impeach <- impeach %>% 
  filter(for_impeachment == "YES") %>% 
  summarise(n())

dem_yes_impeach
dem_no_impeach

```

**Breaking News Story**

In the historic vote to impeach President Donald Trump, House Democrats are split. According to recent data, `r dem_no_impeach` Democrats are currently opposed to impeachment, while `r dem_yes_impeach` Democrats are in favor of impeachment. Democrats are looking to adopt two articles of impeachment against President Trump: abuse of power and obstruction of Congress. Calls for impeachment come in the wake of multiple whistleblower complaints, including those by Lt. Col. Alexander Vindman, a member of the National Security Council. Vindman claims that President Trump demonstrated an abuse of power during a phone call with Ukrainian president Volodymyr Zelenskyy,during which he allegedly threatened to withhold military unless Zelenskyy announced an investigation into former vice president and political opponent Joe Biden.
