---
title: "virginia election database table"
author: "Bryn McLaughlin"
format:
  html:
    self-contained: true
---

#Here is an explorable data table with the results of the 2020 Presidential Election, as well as the 2021 Virginia Gubernatorial Race

![](vaelection_DT.html){fig-align="center"}

#here is code to create a new column to the dataset calculating the difference between the percentage of the vote Youngkin received and what Trump received.

```{r}

```

#Here is a new column to find the Top 5 counties with the highest differences between Younkin/Trump percent, and then create a well-labeled chart to visualize them.

```{r}

```
#Here is a chart that shows the Top 5 counties based on where Youngkin got the highest percentage of the vote.

```{r}

```

#Here is a table that shows the Top 5 counties based on where McCauliffe got the highest percentage of the vote.

```{r}

```

#Here is a finding of your choosing, include a narrative explaing it to the audience and then create either a chart or table displaying it.

```{r}

```

#Here is a second finding of your choosing, include a narrative explaining it to the audience and then create either a chart or table displaying it.

```{r}

```

#Here is a third finding of your choosing, include a narrative explaining it to the audience and then create either a chart or table displaying it.

```{r}

```

