---
title: "Walkthrough Example"
author: "Bryn McLaughlin"
format:
  html:
    self-contained: true
    code-fold: true
    code-tools: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load the packages we'll need
library(tidyverse)
library(lubridate)
library(readxl)
library(writexl)
library(janitor)

```

Below is an example of a grouping, filtering, and summarising walkthrough. I will be using data on how House Democrats voted during the first Trump impeachment proceedings in order to explain the key concepts.

### Load the data

First, we will run the code below to load the data; all of these files should be included in your Posit Cloud directory from the initial Github upload.

Additionally data including election results and demographics are included related to each member's district.

the code below create a data frame called `impeach`, which contains a row for every House Democrat and whether or not the member publicly called for impeachment in the case of the *first* Trump impeachment.

After creating the data frame, we will use the view() function to look at the dataset and understand the different variables.

```{r}

impeach <- readRDS("impeach.rds")

view(impeach)
```

Next we will use the **group_by()** and **summarise()** functions to see how many members in the data set favor impeachment vs. not. After looking through the data set and identiying the needed variables, we will use the `for_impeachment` to pull this information.

Summarise is used at the end to pull the summed number for each variable. When using multiple lines of code, make sure to use the **pipe shortcut** (eg %\>%) to create a complete command.

```{r}

impeach %>% 
  group_by(for_impeachment) %>% 
  summarise(n())


#grouped by for impeachment than summarized
```

Next we will be adding multiple functions to the code we used above. Here we use grouping to break down the Democratic House members by TWO measures: those who are for or against impeachment AND then districts above/below national GDP.

You'll want to ensure you do the grouping on both columns together using the same function, e.g. `group_by(column1, column2).`

```{r}



impeach %>% 
  filter(party == "D") %>% 
  group_by(for_impeachment,gdp_above_national) %>% 
  summarise(n())

#filtered for Dems, grouped by for impeachment and national gdp, then summarized
```

Now we will do the same as above, but this time instead of GDP, group by whether the district is above or below the national average for the percentage of college graduates. The column that captures this information is `pct_bachelors_compared_to_national`.

```{r}


impeach %>% 
  group_by(for_impeachment,pct_bachelors_compared_to_national) %>% 
  summarise(n())

#filtered for Dems, grouped by for impeachment and pct bachelors, then summarized.






```

Now lets try using the **mean()** command.

Instead of counting how many districts are above/below the national average, this time summarize by the MEAN percentage of college grads (located in the column `pct_bachelors`) for districts that are Yes for impeachment vs. No.

We want to end up with the calculated mean for what that percentage is for the Yes districts and the No districts. Therefore we will nest the mean command within the summarise command, and use an extra pair of parentheses to distinguish.

```{r}


impeach %>% 
  filter(party == "D") %>% 
  group_by(for_impeachment) %>% 
  summarise(mean(pct_bachelors))


#filtered for Dems, grouped by for impeachment, then summarized using the mean of percent of pop w bachelors degree.

```

Next we will try grouping by state and filtering for "NO" in for_impeachment. This will show us which states cast the highest number of NO votes.

```{r}

#I want to look at the state breakdown of reps who voted no on impeachment.

impeach %>% 
  filter(for_impeachment=="NO") %>% 
  group_by(state) %>% 
  summarise(n())


#I used this function to explore what states were most prevelent among reps voting NO on impeachment. I filtered for NO, grouped by state, and summarized.

```

Here we can see that 4 Democrat representatives from Texas voted no on impeachment, the highest number among all the states.

Continue to experiment with these commands to find new ways to explore and analyze the data.

This is the end of the tutorial. Thanks!
